Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-28 paper.qmd
Update paper.qmd

Indeed, there is evidence that the era of a single tool dominating an entire analytical pipeline is giving 
way to a more pragmatic approach where researchers combine the complementary 
strengths of multiple languages [@peng2018]. This trend is particularly evident
in the synergistic use of [R]{.proglang}, with its rich ecosystem for statistical modeling, 
[Python]{.proglang}, with its extensive libraries for machine learning, and [Julia]{.proglang} 
for complex simulations through the use of interoperability libraries such as [PythonCall]{.pkg} 
(calling [Python]{.proglang} from [Julia]{.proglang}), [JuliaCall]{.pkg} 
(calling [Julia]{.proglang} from [Python]{.proglang} or [R]{.proglang}), [reticulate]{.pkg} 
(calling [Python]{.proglang} from [R]{.proglang}), [rpy2]{.pkg} and [ryp]{.pkg} (calling [R]{.proglang} from [Python]{.proglang}) [@osborne2024, @navarro2024].
Recent survey data confirms this trend, showing that research scientists use, on average, 
nearly two programming languages in their work, with the [R]{.proglang} and [Python]{.proglang} combination being 
the most prevalent [@chen2025]. This creates a significant challenge for reproducibility:
a project using [R]{.proglang}, [Python]{.proglang}, and system tools like
[Quarto]{.pkg} or \LaTeX requires coordinating multiple, disparate package managers, 
each with its own configuration and potential for conflict and using interoperability
libraries.

>>>>

Indeed, there is evidence that the era of a single tool dominating an entire analytical pipeline is giving 
way to a more pragmatic approach where researchers combine the complementary 
strengths of multiple languages [@peng2018]. This trend is particularly evident
in the synergistic use of [R]{.proglang}, with its rich ecosystem for statistical modeling, 
[Python]{.proglang}, with its extensive libraries for machine learning, and [Julia]{.proglang} 
for complex simulations through the use of interoperability libraries such as [PythonCall]{.pkg} 
(calling [Python]{.proglang} from [Julia]{.proglang}), [JuliaCall]{.pkg} 
(calling [Julia]{.proglang} from [Python]{.proglang} or [R]{.proglang}), [reticulate]{.pkg} 
(calling [Python]{.proglang} from [R]{.proglang}), [rpy2]{.pkg} and [ryp]{.pkg} (calling [R]{.proglang} from [Python]{.proglang}) [@osborne2024; @navarro2024].
Recent survey data confirms this trend, showing that research scientists use, on average, 
nearly two programming languages in their work, with the [R]{.proglang} and [Python]{.proglang} combination being 
the most prevalent [@chen2025]. This creates a significant challenge for reproducibility:
a project using [R]{.proglang}, [Python]{.proglang}, and system tools like
[Quarto]{.pkg} or \LaTeX requires coordinating multiple, disparate package managers, 
each with its own configuration and potential for conflict and using interoperability
libraries.
